Differentially Private Bayesian Inference

### 2018-04-13 main.tex
sensitivity efficiency code
update algorithm setting

@@

\subsubsection{Algorithm Setting Up}
The candidate set and utility function are still the same as before, differ only in the sensitivity. It will output a candidate $r \in R$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 S(x)})$:

@@

 \begin{figure}[h]
    \centering
    \includegraphics[width=1.0\textwidth]{efficiency}
    \label{fig_efficiency}
    \caption{An Experimental Result for Finding the Local Sensitivity efficiently}
    \end{figure}
\subsection{}

>>>>

In our inference algorithm, we take a Dirichlet distribution as $prior$, $\dirichlet(\alpha_1, \alpha_2, \cdots, \alpha_3)$.

@@

\subsubsection{Algorithm Setting up}
The candidate set and utility function are still the same as before, differ only in the sensitivity. It will output a candidate $r \in R$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 S(x)})$:

@@

 \begin{figure}[h]
\centering
\includegraphics[width=1.0\textwidth]{efficiency}
\label{fig_efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\end{figure}

\subsection{Accuracy Study of Algorithms}
\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 200$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_1.eps}}
  \subfigure[Data size $n = 200$ with global $\epsilon = 0.8$]{
    \includegraphics[width=0.48\textwidth]{accuracy_2.eps}} 
\caption{The experimental results of accuracy of four algorithms}
\label{fig_data}
\end{center}
\end{figure*}

We study the accuracy property of the exponential mechanism with three kind of sensitivity, as well as the Laplace mechanism for comparison. As in Fig. \ref{fig_data}, the two figures shown the accuracy of four algorithms under same configuration. The accuracy is measured by Hellinger distance between output $r^*$ and the true inference result $\bysinfer(x)$, $\hlg(r^*, \bysinfer(x))$.
